# Part 5: Results and Conclusion {-}

## Summary of Results {-}


```{r echo = FALSE, warning=FALSE}
fooph <- play_PH %>%
  group_by(startLat)%>%
  filter(n()<2)%>%
  summarise_all(mean) %>%
  arrange(minutes)

fooDC <- play_DC %>%
  group_by(startLat)%>%
  filter(n()<3 )%>%
  summarise_all(mean) %>%
  arrange(minutes)

foony <- play_NY %>%
  group_by(startLat)%>%
  filter(n()<20 )%>%
  summarise_all(mean) %>%
  arrange(minutes)

acity_row <- data.frame(
DC = c(nrow(play_DC), 90000-nrow(play_DC), nrow(fooDC), 100*((nrow(play_DC)+nrow(fooDC))/90000)),
Philly = c(nrow(play_PH),90000 -nrow(play_PH),nrow(fooph), 100*((nrow(play_DC) + nrow(fooph))/90000)),
NYC = c(nrow(play_NY),90000 -nrow(play_NY),nrow(foony),  100*((nrow(play_DC) + nrow(foony))/90000))
)

rownames(acity_row) <- c("Rows Remaining", "Rows NULL","Got through","Total Percent Removed")

x <- as.matrix(acity_row)

```


```{r echo=FALSE, warning=FALSE}
kable(x, "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "float_right")
```

Before diving into this crazy results chart, I need to admit something...I don't know what I'm talking about when it comes to [GIS](https://en.wikipedia.org/wiki/Geographic_information_system). If I were a real maps whiz, I would have limited my city polygons to only include areas people lived. There were issues with several areas within each city. 

  1. Many of these issue areas resulted in, mostly, `NULL` responses from the API I used to get direction routes [^5]. These were easily removed. 
  2. The majority of the rest were a little more *slippery* and got results from the API. An example of one of these were a point in the river would pull `298 NULLS` but would get directions to another random point within the river. These were also easily removed (except for a small few that will be discussed below).
  3. The last bit are a bit more of a question. A question of how evil these made-up gameshow creators are. For example, several points fell into points deep within large philadelphian parks and began with 20-45 minutes of walking. These were kept in[^6].



```{r summary_stats, echo = FALSE, warning = FALSE}
ny_mins_summ <- summary(play_NY$minutes)
ny_mils_summ <- summary(play_NY$miles)

ny_summary_stats <- t(data.frame(ny_mils_summ = as.vector(ny_mils_summ),
                      ny_mins_summ = as.vector(ny_mins_summ)))

colnames(ny_summary_stats) <- c("Min", "1st Qu", "Median", "Mean",
                             "3rd Qu", "Max")

ph_mins_summ <- summary(play_PH$minutes)
ph_mils_summ <- summary(play_PH$miles)

ph_summary_stats <- t(data.frame(ph_mils_summ = as.vector(ph_mils_summ),
                      ph_mins_summ = as.vector(ph_mins_summ)))

colnames(ph_summary_stats) <- c("Min", "1st Qu", "Median", "Mean",
                             "3rd Qu", "Max")

dc_mins_summ <- summary(play_DC$minutes)
dc_mils_summ <- summary(play_DC$miles)

dc_summary_stats <- t(data.frame(dc_mils_summ = as.vector(dc_mils_summ),
                      dc_mins_summ = as.vector(dc_mins_summ)))

colnames(dc_summary_stats) <- c("Min", "1st Qu", "Median",
                                "Mean","3rd Qu", "Max")

acity_summs <- t(rbind(dc_summary_stats, ny_summary_stats, ph_summary_stats))
acity_summs1 <- as.data.frame(acity_summs)
acity_summs1 <-  acity_summs1[c(2, 6,4,1,5,3)]
 
colnames(acity_summs1) <- c("DC minutes","Philly minutes","NYC minutes", "DC miles", "Philly miles", "NYC miles")

##sds for all
x <- data.frame(
  q <- sd(play_DC$minutes),
  w <- sd(play_PH$minutes),
  e <- sd(play_NY$minutes),
  a <- sd(play_DC$miles),
  s <- sd(play_PH$miles),
  d <- sd(play_NY$miles))

colnames(x) <- c("DC minutes","Philly minutes","NYC minutes", "DC miles", "Philly miles", "NYC miles")

acity_summs1 <- rbind(acity_summs1, x)
rownames(acity_summs1) <-  c("Min", "1st Qu", "Median", "Mean",
                             "3rd Qu", "Max", "St. Dev.")

acity_summs1 %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE, position = "float_right")
```

So let's start off by congratulating our nation's capital with running away with the competition. Everything about their summary statistics tells the game show contestents to hope to see `Washington DC` next to their assigned coordinates.

New York City and Philadelphia are actually in pretty close in everything related to time. Unfortunatly the average milage trip in NYC was 9 miles (and 12 in the 3rd quartile) longer than in Philly! So, if you're a real resident of NYC, you're getting some value for your time.

The only two concerning items are the Maxs and Standard Deviations' of New York and Philadelphia. 

## Visual Exploration {-}

```{r scatterplots, echo = FALSE, fig.width=10}
DCscatter <- ggplot() +
  geom_point(data = play_DC, aes(x = miles, y = minutes),
                                     color = "#ff7400") +
  ggtitle("DC")+
  theme(legend.position="none")

PHscatter <- ggplot() +
  geom_point(data = play_PH, aes(x = miles, y = minutes),
                                     color = "#F14628") +
  ggtitle("Philly")+
  theme(legend.position="none")

NYscatter <- ggplot() +
  geom_point(data = play_NY, aes(x = miles, y = minutes),
                                     color = "#2360a5") +
  ggtitle("NYC")+
  theme(legend.position="none")

```

```{r histograms, echo = FALSE, message= FALSE, fig.width=10}
DChisto <- ggplot() +
  geom_histogram(data = play_DC, aes(x = minutes),fill = "#ff7400") +
  ggtitle("DC")+
  theme(legend.position="none")

PHhisto <- ggplot() +
  geom_histogram(data = play_PH, aes(x = minutes),fill = "#F14628") +
  ggtitle("Philly")+
  theme(legend.position="none")

NYhisto <- ggplot() +
  geom_histogram(data = play_NY, aes(x = minutes),fill = "#2360a5") +
  ggtitle("NYC")+
  theme(legend.position="none")

```

```{r , echo = FALSE, message= FALSE, fig.width=10, fig.height = 10}
grid.arrange(DChisto, PHhisto, NYhisto,DCscatter, PHscatter, NYscatter, ncol = 3)

```


```{r echo=FALSE, warning=FALSE}
df <- data.frame(
  DC = c(68.34, 61.05,7.29 ),
  Philly = c(142.7, 134.1, 8.6),
  NYC = c(468.5, 302.6, 165.8)
)

rownames(df) <- c("Total Area", "Land Area", "Water Area")

kable(df, "html") %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "float_right")
```



As suspected, we can see some Right Tail Extremes in the histograms of minutes for both NYC and Philadelphia. On the other hand, DC what a beauty. What causes this? My hypothesis is that it has to do with the size differences between the cities. You can see this in the table of Areas. This also, I think, helps explain the appearance of more`NULL` values in the Philadelphia and New York routes because of the much larger amount of water area within city limits.

Talk about skew here more. Maybe even a table.

## Evil Points {-}

In order to look at these outliers within the NYC and Philly dataset, I would like to put forward an axiom:

> Any trip over three hours, in this situation, can be defined as "Shit Luck", and any trip over five hours is straight up Evil.

Below I've split the histograms up to show these three different types of trips. normal trips (less than 3 hours) are in light blue, bad trips are in dark blue (3 - 5 hours), and truly evil points in black (5+ hours).

```{r scatter_badpoints_id, echo=FALSE, fig.width=10}

foo <- play_PH %>%
  mutate(comfort = ifelse(minutes >= 300, "evil",
              ifelse(minutes < 300 & minutes >= 181, "bad","normal"
                     )))

foo1 <- play_NY %>%
  mutate(comfort = ifelse(minutes >= 300, "evil",
              ifelse(minutes < 300 & minutes >= 181, "bad","normal"
                     )))

NYscatter2 <- ggplot() +
  geom_point(data = foo1, aes(x = miles, y = minutes, color = comfort))+
  scale_color_manual(values=c( "#0f16a8","black","#32a1fc"))+
  ggtitle("NYC")+
  theme(legend.position="none")

PHscatter2 <- ggplot() +
  geom_point(data = foo, aes(x = miles, y = minutes, color = comfort))+
  scale_color_manual(values=c( "#0f16a8","black","#32a1fc"))+
  ggtitle("PH")+
  theme(legend.position="none")

DCscatter2 <- ggplot() +
  geom_point(data = play_DC, aes(x = miles, y = minutes),
                                     color = "#32a1fc") +
  ggtitle("DC")+
  theme(legend.position="none")

grid.arrange(DCscatter2, PHscatter2, NYscatter2, ncol = 3)

```
<br>
<br>

```{r shit_trips,echo = FALSE,  warning = FALSE}
badluck_ny <- play_NY %>%
  filter(minutes >=180) 

badluck_ph <- play_PH %>%
  filter(minutes >= 180)

badluck_dc <- play_DC %>%
  filter(minutes >= 180)
#Two hours
badluck_ny1 <- play_NY %>%
  filter(minutes >=120) 

badluck_ph1 <- play_PH %>%
  filter(minutes >= 120)

badluck_dc1 <- play_DC %>%
  filter(minutes >= 120)

#percent of trips that are absurd
df <- data.frame(DC =
round((nrow(badluck_dc)/nrow(play_DC))*100, digits = 2),
PH = 
round((nrow(badluck_ph)/nrow(play_PH))*100, digits = 2),
NY = 
round((nrow(badluck_ny)/nrow(play_NY))*100, digits = 2))

df1 <- data.frame(DC =
round((nrow(badluck_dc1)/nrow(play_DC))*100, digits = 2),
PH = 
round((nrow(badluck_ph1)/nrow(play_PH))*100, digits = 2),
NY = 
round((nrow(badluck_ny1)/nrow(play_NY))*100, digits = 2))

df <- rbind(df1, df)
rownames(df) <- c( "2 hour trip", "3 hour trip")

```

###Percent of Bad Trips {-}
```{r shit_trips_table, echo=FALSE, warning=FALSE}
kable(df, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE, position = "float_right")

```

What we see here is that most of the bad points are not truly evil (only 8% and 6% respectively). So, what are those points? I've decided to restrict these points to being above 400 minutes (you'll see why in a second).

### NYC Evil Trips

```{r, echo = FALSE}

evil <- play_NY %>%
  filter(minutes >400)

#GGPLOT
foopath <- evil %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))

foopath1 <-evil %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))

foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along <- gg_ny +
  geom_point(data = foopath, aes(x = longitude, y = latitude), color = "#fdf5e6",  size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

###LEAFLET
leaf_ny <- 
leaflet(ny) %>%
  addPolygons(fillColor = "#8a07ef", weight = 1, smoothFactor = 0.2,
              opacity = 0.5 ,color = "white")%>%
  addProviderTiles("Esri.WorldStreetMap") %>%
  addCircleMarkers(lng = evil$startLon, lat = evil$startLat,
                  radius = 2, color = "red")
```

```{r echo = FALSE}
along
leaf_ny
```
<br>

So we can see that all `298` trips that are above are from a singular location. Furthermore, the mean of those trips is a staggering `r round(mean(evil$minutes), digits = 2)`.

### Philadelphia Evil Trips

```{r echo = FALSE}
evil <- play_PH %>%
  filter(minutes >400)

#GGPLOT
foopath <- evil %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <-evil %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along <- gg_ph +
  geom_point(data = foopath, aes(x = longitude, y = latitude, color = type), size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

# can see 2-3 bad bad points

evil_ph_5 <- data.frame(
  latitude = c(39.88880, 39.90100, 40.05352,39.88880 ,39.89117),
  longitude =c(-75.20997, -75.21456, -75.23903, -75.20997, -75.14090)
)

leaflet_ph <- 
leaflet(philly) %>%
  addPolygons(fillColor = "#8a07ef", weight = 1, smoothFactor = 0.2,
              opacity = 0.5 ,color = "white")%>%
  addTiles() %>%
  addCircleMarkers(lng = evil_ph_5$longitude, lat = evil_ph_5$latitude,
                   radius = 2, color = "blue")


```

```{r echo = FALSE}
along
leaflet_ph
```

```{r shit_trips_table_philly, echo=FALSE, warning=FALSE}
tab_evil <- aggregate(evil[,1], list(evil$startLat), length)%>%
  arrange(desc(x))

tab_evil1 <- aggregate(evil[,1], list(evil$endLat), length)%>%
  arrange(desc(x))

tab_evil <- cbind(tab_evil[1:50,], tab_evil1[1:50,])
colnames(tab_evil) <- c("Bad Origin", "count", "Bad Destination", "count")
tab_evil <- tab_evil[1:5,]


kable(tab_evil, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE, position = "float_right")

```
<br>
<br>
So, unlike NYC, Philadelphia has several locations that are either hard to get to or from. This is apparent from the table to the right.


<br>
## Results of Trips < 3 Hours {-}

Let's say, for no reason at all, that the gameshow guarantees that no trip will be more than 3 hours. How do the results change?


```{r reduced_scatter, echo = FALSE, fig.width=10}
goodluck_ny <- play_NY %>%
  filter(minutes <=250) 

goodluck_ph <- play_PH %>%
  filter(minutes <= 250)

PHscatter1 <- ggplot() +
  geom_point(data = goodluck_ph, aes(x = miles, y = minutes),
                                     color = "#F14628") +
  ggtitle("Philly")+
  theme(legend.position="none")

NYscatter1 <- ggplot() +
  geom_point(data = goodluck_ny, aes(x = miles, y = minutes),
                                     color = "#2360a5") +
  ggtitle("NYC")+
  theme(legend.position="none")

PHhisto2 <- ggplot() +
  geom_histogram(data = goodluck_ph, aes(x = minutes),fill = "#F14628") +
  ggtitle("Philly")+
  theme(legend.position="none")

NYhisto2 <- ggplot() +
  geom_histogram(data = goodluck_ny, aes(x = minutes),fill = "#2360a5") +
  ggtitle("NYC")+
  theme(legend.position="none")

```


```{r , echo = FALSE, message= FALSE, fig.width=10, fig.height = 10}
grid.arrange(DChisto, PHhisto2, NYhisto2,DCscatter, PHscatter1, NYscatter1, ncol = 3)

```


```{r echo = FALSE}
acity_dat <- play_DC

foo <- acity_dat %>%
  arrange(minutes)
#getting 10% of rows
x <- nrow(foo)*.1

foo <- foo[1:x,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_short_dc <- gg_dc +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

#######
#getting top 10% sample
foo <- acity_dat %>%
  arrange(desc(minutes))

#getting 10% of rows
x <- nrow(foo)*.1

foo <- foo[1:x,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_long_dc <- gg_dc +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")


#some of the middle

foo <- acity_dat %>%
  arrange(desc(minutes))
#getting 10% of rows
x <- (nrow(foo)*.1)*.5

x <- (0.5*nrow(acity_dat))-x
y <- (0.5*nrow(acity_dat))+x

foo <- foo[x:y,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_med_dc <- gg_dc +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

```


```{r echo = FALSE}

acity_dat <- play_PH

foo <- acity_dat %>%
  arrange(minutes)
#getting 10% of rows
x <- nrow(foo)*.1

foo <- foo[1:x,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_short_ph <- gg_ph +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

#######
#getting top 10% sample
foo <- acity_dat %>%
  arrange(desc(minutes))

#getting 10% of rows
x <- nrow(foo)*.1

foo <- foo[1:x,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_long_ph <- gg_ph +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")


#some of the middle

foo <- acity_dat %>%
  arrange(desc(minutes))
#getting 10% of rows
x <- (nrow(foo)*.1)*.5

x <- (0.5*nrow(acity_dat))-x
y <- (0.5*nrow(acity_dat))+x

foo <- foo[x:y,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_med_ph <- gg_ph +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

```



```{r echo = FALSE}


acity_dat <- play_NY

foo <- acity_dat %>%
  arrange(minutes)
#getting 10% of rows
x <- nrow(foo)*.1

foo <- foo[1:x,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_short_ny <- gg_ny +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

#######
#getting top 10% sample
foo <- acity_dat %>%
  arrange(desc(minutes))

#getting 10% of rows
x <- nrow(foo)*.1

foo <- foo[1:x,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_long_ny <- gg_ny +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")


#some of the middle

foo <- acity_dat %>%
  arrange(desc(minutes))
#getting 10% of rows
x <- (nrow(foo)*.1)*.5

x <- (0.5*nrow(acity_dat))-x
y <- (0.5*nrow(acity_dat))+x

foo <- foo[x:y,]%>%
  sample_n(50) 

foopath <- foo %>%
  select(latitude = endLat, longitude = endLon, trip_id) %>%
  mutate(type = rep("destination"))
foopath1 <- foo %>%
  select(latitude = startLat, longitude = startLon, trip_id) %>%
  mutate(type = rep("origin"))
foopath <- rbind(foopath, foopath1)
foopath$type <- as.factor(foopath$type) 
foopath$trip_id <- as.factor(foopath$trip_id)

along_med_ny <- gg_ny +
  geom_point(data = foopath, aes(x = longitude, y = latitude),color = "#fdf5e6", size = 1.5)+
  geom_path(data=foopath, aes(x=longitude, y=latitude, group=trip_id), color = "#fdf5e6", size=0.4)+
  theme(legend.position="none")

```

### Sample of Short, Medium, and Long Trips {-}
I wanted to see what some of the different length trips looked like in each city. Below is series of graphs showing short, medium, and long trips. This was done by taking sample of 50 trips from the bottom, middle, and top 10% of trips for each city.

```{r echo = FALSE, fig.height = 10, fig.width = 12}
grid.arrange(along_short_dc,along_med_dc, along_long_dc,
             along_short_ph,along_med_ph, along_long_ph,
             along_short_ny,along_med_ny, along_long_ny, ncol = 3)
```


##Neighborhoods {-}

As a last question, I was wondering where within each city was the best origin. Below are the top ten origins.

```{r echo = FALSE}
##Philly

foo <- play_PH %>%
  group_by(startLat)%>%
  filter(n()>2)%>%
  summarise_all(mean) %>%
  arrange(minutes)


#the winner has 1 trip and is delaware rive to delaware river and takes ~20 minutes
head_neighborhoods_ph <- data.frame(
        latitude = foo$startLat[1:10],
        longitude =foo$startLon[1:10])

along <- gg_ph +
  geom_point(data = head_neighborhoods_ph, aes(x = longitude, y = latitude), color = "#fdf5e6",  size = 1.5)


leaf_ph_neigh <- 
  leaflet(philly) %>%
  addPolygons(fillColor = "#8a07ef", weight = 1, smoothFactor = 0.2,
              opacity = 0.5 ,color = "white")%>%
  addProviderTiles("Esri.WorldStreetMap") %>%
  addCircleMarkers(lng = head_neighborhoods_ph$longitude, lat = head_neighborhoods_ph$latitude,
                   radius = 2, color = "red")

leaf_ph_neigh

```

<br>

```{r echo = FALSE}
###DC

foo <- play_DC %>%
  group_by(startLat)%>%
  filter(n()>3 )%>%
  summarise_all(mean) %>%
  arrange(minutes)


#the winner has 1 trip and is delaware rive to delaware river and takes ~20 minutes
head_neighborhoods_dc <- data.frame(
  latitude = foo$startLat[1:10],
  longitude =foo$startLon[1:10])

along <- gg_dc +
  geom_point(data = head_neighborhoods_dc, aes(x = longitude, y = latitude), color = "#fdf5e6",  size = 1.5)


leaf_dc_neigh <- 
  leaflet(dc) %>%
  addPolygons(fillColor = "#8a07ef", weight = 1, smoothFactor = 0.2,
              opacity = 0.5 ,color = "white")%>%
  addProviderTiles("Esri.WorldStreetMap") %>%
  addCircleMarkers(lng = head_neighborhoods_dc$longitude, lat = head_neighborhoods_dc$latitude,
                   radius = 2, color = "red")

leaf_dc_neigh
```

<br>

```{r echo = FALSE}
###NY

foo <- play_NY %>%
  group_by(startLat)%>%
  filter(n()>20 )%>%
  summarise_all(mean) %>%
  arrange(minutes)

#the winner has 1 trip and is delaware rive to delaware river and takes ~20 minutes
head_neighborhoods_ny <- data.frame(
  latitude = foo$startLat[1:10],
  longitude =foo$startLon[1:10])

along <- gg_ny +
  geom_point(data = head_neighborhoods_ny, aes(x = longitude, y = latitude), color = "#fdf5e6",  size = 1.5)


leaf_ny_neigh <- 
  leaflet(ny) %>%
  addPolygons(fillColor = "#8a07ef", weight = 1, smoothFactor = 0.2,
              opacity = 0.5 ,color = "white")%>%
  addProviderTiles("Esri.WorldStreetMap") %>%
  addCircleMarkers(lng = head_neighborhoods_ny$longitude, lat = head_neighborhoods_ny$latitude,
                   radius = 2, color = "red")

leaf_ny_neigh
```



[^4]: This includes some absurd shit like within rivers and oceans.
[^5]: I used the [HERE API](https://developer.here.com/)
[^6]: In this made-up world, I guess I'm the Evil Game Show creator. Shame for the contestents I guess....